Generality in food webs scales with species richness, not latitude

### 2015-01-27 manuscript/latitudepaper.tex
unknown changes

In this data set, none of the best fit models for species richness, connectance, or links per species included an 
effect of latitude on either the scaling exponent or residual (Table \ref{Bestfits}). 
$G$ increased slightly in more recent webs ($\rho_{2}$=0.005, $p$\textless0.001), but the best-fit models for $V$ and $Z$ did not include a term for year of publication. 
In contrast, $Z$ and $V$ were higher in lake food webs ($\beta_{4}$=0.10, $p$\textless0.001 and $\beta_{4}$=0.10, $p$\textless0.001, respectively) while the best-fit model for $G$ did not include an effect for any ecosystem type.

>>>>

In this data set, the best fit models for species richness and links per species did not include an 
effect of latitude on either the scaling exponent or residual (Table \ref{Bestfits}). 
$G$ increased slightly in more recent webs ($\rho_{2}$=0.005, $p$\textless0.001), but the best-fit models for $V$ and $Z$ did not include a term for year of publication. 
In contrast, $Z$ and $V$ were higher in lake food webs ($\beta_{4}$=0.10, $p$\textless0.001 and $\beta_{4}$=0.10, $p$\textless0.001, respectively) while the best-fit model for $G$ did not include an effect for any ecosystem type.
